---
title: "9041 Assignment 2"
author: Layla Hussain
date: today
format: 
    html:
      toc: true
      code-fold: true
      code-summary: "Show code"
      df-print: paged
execute:
    echo: false
    warning: false
---

```{r packages}
#| output: FALSE

library(tidyverse)
library(readxl)
library(psych)
library(gt)
library(janitor)

```

```{r loading data}
#| output: FALSE

data <- read_excel("./Attachment_Anxiety_Data.xlsx")

head(data)

```

```{r, data cleaning}
#| output: FALSE

# Assigning more informative labels for gender and relationship. Plus, changing all survey responses to integers. 

attachment_clean <- data |> 
  mutate(Gender = case_when(Gender == 1 ~ "Male", Gender == 2 ~ "Female")) |>
  
  mutate(Relationship = case_when(Relationship == 1 ~ "Married",
                                  Relationship == 2 ~ "In a relationship",
                                  Relationship == 4 ~ "Divorced",
                                  Relationship == 5 ~ "In a relationship",
                                  Relationship == 6 ~ "Never in a relationship",
                                  Relationship == 7 ~ "Prefer not to say",)) |>
  
    mutate_at(7:45, as.integer)

```

```{r, score items}
#| output: FALSE

#SA = Social Interaction Anxiety Scale Question 1 = social_anxiety 
#AA = Experiences in Close Relationships Anxiety Subscale Question 1 = relationships_subscale
#SEst = Rosenberg Self-Esteem Scale Question 1 = rosenberg

keys <- list(
              social_anxiety = c("SA_1", "SA_2", "SA_3", "SA_4", "-SA_5", "SA_6", "SA_7", "SA_8", "-SA_9", "SA_10", "-SA_11", "SA_12", "SA_13", "SA_14", "SA_15", "SA_16", "SA_17", "SA_18", "SA_19", "SA_20"),
             
              relationships_subscale = c("AA_1", "-AA_2", "AA_3", "AA_4", "-AA_5", "-AA_6", "AA_7", "-AA_8", "-AA_9"),
             
             rosenberg = c("SEst_1", "SEst_2", "SEst_3", "SEst_4", "SEst_5", "SEst_6", "SEst_7", "SEst_8", "SEst_9", "SEst_10"))

social_anxiety_scores <- scoreItems(keys["social_anxiety"], attachment_clean, totals = F, min = 0, max = 4)

relationships_subscale_scores <- scoreItems(keys["relationships_subscale"], attachment_clean, totals = F, min = 1, max = 7)

rosenberg_scores <- scoreItems(keys["rosenberg"], attachment_clean, totals = F, min = 1, max = 4)

social_anxiety_df <- as.data.frame(social_anxiety_scores$scores)
relationships_subscale_df <- as.data.frame(relationships_subscale_scores$scores)
rosenberg_df <- as.data.frame(rosenberg_scores$scores)

allscores_df <- cbind(social_anxiety_df, relationships_subscale_df, rosenberg_df)

```

```{r, combine data frames}
#| output: FALSE

attachment_clean <- cbind(attachment_clean, allscores_df)

head(attachment_clean)

```

```{r, reduced data}
#| output: FALSE

attachment_final <- attachment_clean |>
  select("Gender", "Relationship", "social_anxiety", "relationships_subscale", "rosenberg")|>
  mutate_if(is.numeric, round, 2)
  
```

```{r, reproducible table for relationship type distribution}
#| output: FALSE

demo_table <- attachment_final |>
  tabyl(Gender, Relationship)

gttable <- demo_table |>
  gt() |>
  tab_header(
    title = md("*Distribution of Relationship Status by Gender*")
  )

print(gttable)


```

```{r, reproducible table for attachment new dataframe}
#| output: FALSE

# Cronbach alpha to 2 decimal places
alphas <- c(
  social_anxiety = social_anxiety_scores$alpha,
  relationships = relationships_subscale_scores$alpha,
  rosenberg = rosenberg_scores$alpha
)

alphas <- round(alphas, 2)

# Summary statistics
summary <- describe(select(attachment_final, social_anxiety:rosenberg))

# Label sample size 
n <- (describe(attachment_final))[1,2]

Scales <- c(
  "Social Interaction Anxiety Scale",
  "Experiences in Close Relationships Anxiety Subscale",
  "Rosenberg Self-Esteem Scale"
)

summary$Scales <- Scales

summary <- summary |>
  select(Scales, mean, median, sd, range) |>
  mutate_if(is.numeric, round, 2)

summary$alpha <- alphas

gttable.2 <- gt(summary) |>
  tab_header(
    title = md("*Descriptive Statistics for Three Scales Assessing Attachment and Social Anxiety*")
  )|>
    cols_label(
        mean = "Mean",
        median = "Median",
        sd = "SD",
        range = "Range",
        alpha = "Cronbach's Alpha")

print(gttable.2)

```


```{r, filtered dataset}
#| output: FALSE

attachment_filt <- attachment_final |>
    filter(Gender == "Female")

# Checking
table(attachment_filt$Gender) 

```

```{r, reproducible table for FILTERED attachment new dataframe}
#| output: FALSE

# Cronbach alpha to 2 decimal places

filt_alphas <- c(
  social_anxiety = social_anxiety_scores$alpha,
  relationships = relationships_subscale_scores$alpha,
  rosenberg = rosenberg_scores$alpha
)

filt_alphas <- round(filt_alphas, 2)

# Summary statistics
filt_summary <- describe(select(attachment_filt, social_anxiety:rosenberg))

# Label sample size 
n <- (describe(attachment_filt))[1,2]

Scales <- c(
  "Social Interaction Anxiety Scale",
  "Experiences in Close Relationships Anxiety Subscale",
  "Rosenberg Self-Esteem Scale"
)

filt_summary$Scales <- Scales

filt_summary <- filt_summary |>
  select(Scales, mean, median, sd, range) |>
  mutate_if(is.numeric, round, 2)

filt.reptable <- cbind(filt_summary, filt_alphas)

gttable.3 <- gt(filt.reptable) |>
  tab_header(
    title = md("*Descriptive Statistics for Women's Responses to Three Scales Assessing Attachment and Social Anxiety*")
  )|>
    cols_label(
        mean = "Mean",
        median = "Median",
        sd = "SD",
        range = "Range",
        filt_alphas = "Cronbach's Alpha")

print(gttable.3)

```

## Intro

## Methods

### Participants

In this data set there were `{r} n` participants, with varying distributions of education type (Table 1).

`{r} gttable`

### Measures

In this Attachment and social anxiety dataset, there are responses to three scales. They are 1) The Social Interaction Anxiety Scale which measures individual's anxiety during social interaction (Cronbach's alpha = `{r} alphas[1]`). 2) The subscale of the Experiences in Close Relationships Scale which measures individual's anxiety in relationships (Cronbach's alpha = `{r} alphas[2]`). 3) The Rosenberg Self-Esteem Scale which measures self-worth (Cronbach's alpha = `{r} alphas[3]`). 

### Data Analysis Strategy

To correctly assess responses, items 5, 9, and 11 from the Social Interaction Anxiety Scale, and items 2, 5, 6, 8, and 9 from the Rosenberg Self-Esteem Scale were reverse keyed. 

## Results

`{r} gttable.2`

This table (Table 2) presents the mean, median, standard deviation, range, and Cronbach’s alpha for each scale in the full sample. Participants had a mean social interaction anxiety score of `{r} summary[1,2]`, a mean relationship anxiety score of `{r} summary[2,2]`, and a mean self-esteem score of `{r} summary[3,2]`.

`{r} gttable.3`


This table (Table 3) presents the mean, median, standard deviation, range, and Cronbach’s alpha for each scale, this time, the data are filtered to only show responses from Female participants. Female participants had a mean social interaction anxiety score of `{r} filt_summary[1,2]`, a mean relationship anxiety score of `{r} filt_summary[2,2]`, and a mean self-esteem score of `{r} filt_summary[3,2]`.


## Discussion